SaPaFigures

### 2022-03-25 R/PaperFigures.Rmd
saved figures for paper as EPS

PlotHistSumFinalViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                scale = "width", trim = T, position = position_dodge(width = .85) ,
                aes(x=as.factor(LogBin),y=.data[[y_var]], linetype =.data[[colorStrain]]))+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], group =.data[[colorStrain]],shape = CultureRegion),
               size=3, position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = .75))+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .6,position = position_dodge(width = .75) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c( 16,17,1,2))+
    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotHistSumFinalViolin(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            "NormalizedFrequency", "Culture")
HistCondRegionSum = HistCondRegionSum %>% unite(CultureRegion, Culture, Region, sep = " ", remove = FALSE)

@@

PlotAggCoreViolinFacet<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=.data[[colorStrain]],y=.data[[y_var]], linetype =.data[[colorStrain]]),
               position = position_dodge(width = 0.75),show.legend = T)+
    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
               aes(x=.data[[colorStrain]],ymin=.data[[y_var]],ymax=.data[[y_var]]),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=.data[[colorStrain]],y=.data[[y_var]],  shape =CultureRegion),size=4, position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c( 16,17,1,2))+
    #scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_x_discrete(labels = c("Mono-infection","Co-infection"))+
    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotAggCoreViolinFacet(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             plankAggHistCond%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "Culture", "Species")

PlotAggCoreViolin<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=.data[[facet]],y=.data[[y_var]], linetype =.data[[colorStrain]]),
               position = position_dodge(width = 0.75),show.legend = T)+
    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
               aes(x=.data[[facet]],ymin=.data[[y_var]],ymax=.data[[y_var]], group = Culture),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=.data[[facet]],y=.data[[y_var]],  group= Culture, shape =CultureRegion),size=4, 
               position = position_jitterdodge(jitter.height = 0, jitter.width = .2,dodge.width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    #facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c( 16,17,1,2))+
    #scale_color_grey(labels = c("Mono-infection","Co-culture"))+
    scale_x_discrete(labels = c(bquote(italic('P. aeruginosa')),bquote(italic('S. aureus'))))+
    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotAggCoreViolin(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             plankAggHistCond%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "Culture", "Species")
#####
### Mutants
PlotAggCoreMut<-function(rep.df,region.df, y_var, title,colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=Region,y=.data[[y_var]], shape = Region, color =.data[[colorStrain]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
    geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=Region,ymin=.data[[y_var]],ymax=.data[[y_var]], group =Strain),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
     #          aes(x=Region,y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    ggtitle(title)+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotAggCoreMut(plankAggHistRep%>% filter(Culture=="co") %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
             plankAggHistCond%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "", "Strain", "Species")

@@

PlotwtED2()
#####
#Figure 2F
PlotEDvsDensityFinal<-function(df, yAxis,tittle){
  ggplot()+
    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], color= Strain, shape =Region ),size=4)+
    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
    geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
    #geom_text(x=.3, y=10, label= "bl")+
    annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
    #geom_abline(intercept = 9.519, slope = 50.800, color = "Red")+
    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
    scale_shape_manual(values=c(16, 17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotEDvsDensityFinal(EdSlice %>% filter(Strain == "wt"), "TotalRatio","")
PlotEDvsDensityFinal2<-function(df, yAxis,tittle){
  ggplot()+
    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], color= Strain, shape =Region ),size=4)+
    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
    #geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
    #geom_text(x=.3, y=10, label= "bl")+
    #annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
    scale_color_manual(values=c("#000000", "#D34328", "#3964C3"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
    #geom_abline(intercept = 9.519, slope = 50.800, color = "Black")+
    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
    scale_shape_manual(values=c(16, 17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

PlotEDvsDensityFinal2(EdSlice, "TotalRatio","")

>>>>

HistCondRegionSum = HistCondRegionSum %>% unite(CultureRegion, Culture, Region, sep = " ", remove = FALSE)
PlotHistSumFinalViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                scale = "width", trim = T, position = position_dodge(width = .85) ,
                aes(x=as.factor(LogBin),y=.data[[y_var]], linetype =.data[[colorStrain]]))+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], group =.data[[colorStrain]],shape = CultureRegion),
               size=3, position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = .75))+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .6,position = position_dodge(width = .75) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c( 16,17,1,2))+
    scale_linetype_manual(values=c( "solid","solid"),labels = c("Mono-infection","Co-infection"))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+

    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"),#facet background
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
}

Figure2C<-PlotHistSumFinalViolin(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            "NormalizedFrequency", "Culture")

ggsave(plot = Figure2C,
       file="/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/EPS Figures/Figure2C.EPS",
device = cairo_ps, 
width = 25,
height = 10, 
units = "cm")

@@

PlotAggCoreViolinFacet<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=.data[[colorStrain]],y=.data[[y_var]], linetype =.data[[colorStrain]]),
               position = position_dodge(width = 0.75),show.legend = T)+
    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
               aes(x=.data[[colorStrain]],ymin=.data[[y_var]],ymax=.data[[y_var]]),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=.data[[colorStrain]],y=.data[[y_var]],  shape =CultureRegion),size=4, position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c( 16,17,1,2))+
    #scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_x_discrete(labels = c("Mono-infection","Co-infection"))+
    scale_linetype_manual(values=c( "solid","solid"),labels = c("Mono-infection","Co-infection"))+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotAggCoreViolinFacet(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             plankAggHistCond%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "Culture", "Species")

PlotAggCoreViolin<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=.data[[facet]],y=.data[[y_var]], linetype =.data[[colorStrain]]),
               position = position_dodge(width = 0.75),show.legend = T)+
    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
               aes(x=.data[[facet]],ymin=.data[[y_var]],ymax=.data[[y_var]], group = Culture),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=.data[[facet]],y=.data[[y_var]],  group= Culture, shape =CultureRegion),size=4, 
               position = position_jitterdodge(jitter.height = 0, jitter.width = .2,dodge.width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    #facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c( 16,17,1,2))+
    #scale_color_grey(labels = c("Mono-infection","Co-culture"))+
    scale_x_discrete(labels = c(bquote(italic('P. aeruginosa')),bquote(italic('S. aureus'))))+
    scale_linetype_manual(values=c( "solid","solid"),labels = c("Mono-infection","Co-infection"))+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"),#facet background
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
}
Figure2D<-PlotAggCoreViolin(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             plankAggHistCond%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "Culture", "Species")

ggsave(Figure2D, file="/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/EPS Figures/Figure2D.EPS", device="eps", width = 5.5, height = 4.5)
#####
### Mutants
PlotAggCoreMut<-function(rep.df,region.df, y_var, title,colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=Region,y=.data[[y_var]], shape = Region, color =.data[[colorStrain]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
    geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=Region,ymin=.data[[y_var]],ymax=.data[[y_var]], group =Strain),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
     #          aes(x=Region,y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    ggtitle(title)+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotAggCoreMut(plankAggHistRep %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Aggregation=="Planktonic"),
             plankAggHistCond%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "", "Strain", "Species")

PlotAggCoreViolinFacetMut<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=.data[[colorStrain]],y=.data[[y_var]], color =.data[[colorStrain]]),
               position = position_dodge(width = 0.75),show.legend = T)+
    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
               aes(x=.data[[colorStrain]],ymin=.data[[y_var]],ymax=.data[[y_var]]),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=.data[[colorStrain]],y=.data[[y_var]],  color = .data[[colorStrain]],shape =Region),size=4, position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c( 16,17,1,2))+
    scale_color_manual(values=c("#000000", "#D34328", "#3964C3"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    scale_x_discrete(labels = c("","",""))+
    #scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"),#facet background
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
}

Figure3C<-PlotAggCoreViolinFacetMut(plankAggHistRep%>% filter(Culture=="co") %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
             plankAggHistCond%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "Strain", "Species")

ggsave(Figure3C, file="/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/EPS Figures/Figure3C.EPS", device="eps", width = 7.5, height = 4.5)

@@

PlotwtED2()
#####
#Figure 2F
PlotEDvsDensityFinal<-function(df, yAxis,tittle){
  ggplot()+
    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], color= Strain, shape =Region ),size=4)+
    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
    geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
    #geom_text(x=.3, y=10, label= "bl")+
    annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
    #geom_abline(intercept = 9.519, slope = 50.800, color = "Red")+
    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
    scale_shape_manual(values=c(16, 17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotEDvsDensityFinal(EdSlice %>% filter(Strain == "wt"), "TotalRatio","")

PlotEDvsDensityFinal2<-function(df, xAxis,tittle){
  ggplot()+
    geom_point(data = df,aes(x=.data[[xAxis]],y=WmeanDist, color= Strain, shape =Region ),size=4)+
    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
    #geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
    #geom_text(x=.3, y=10, label= "bl")+
    #annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
    scale_color_manual(values=c("#000000", "#D34328", "#3964C3"),
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
    #geom_abline(intercept = 9.519, slope = 50.800, color = "Black")+
    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
    scale_shape_manual(values=c(16, 17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

PlotEDvsDensityFinal2(EdSlice, "TotalRatio","")
write.csv(EdSlice,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BacterialSaturationData.csv", row.names = T)
